---
<<<<<<< HEAD
<<<<<<< HEAD
output: 
    github_document:
      toc: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
=======
title: "R package for a new beta-type copula: rMGLReg"
=======
>>>>>>> parent of 0dd254f (v2)
output: 
    github_document:
      toc: true
---

<<<<<<< HEAD
<!-- # rMGLReg -->

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/lizhengxiao/rMGLReg/branch/main/graph/badge.svg)](https://codecov.io/gh/lizhengxiao/rMGLReg?branch=main)
[![R-CMD-check](https://github.com/lizhengxiao/rMGLReg/workflows/R-CMD-check/badge.svg)](https://github.com/lizhengxiao/rMGLReg/actions)
<!-- badges: end -->


>>>>>>> parent of 49cec11 (Merge pull request #20 from lizhengxiao/main)
=======
<!-- README.md is generated from README.Rmd. Please edit that file -->
>>>>>>> parent of 0dd254f (v2)

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<<<<<<< HEAD
<<<<<<< HEAD
# rMGLReg

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/lizhengxiao/rMGLReg/branch/main/graph/badge.svg)](https://app.codecov.io/gh/lizhengxiao/rMGLReg?branch=main)
[![R-CMD-check](https://github.com/lizhengxiao/rMGLReg/workflows/R-CMD-check/badge.svg)](https://github.com/lizhengxiao/rMGLReg/actions)
<!-- badges: end -->

The goal of rMGLReg is to 

- provide a nice visualization tool for interpreting the MGL copula and MGL-EV copula, along with its survival copulas.

- show the maximum likelihood (ME) estimation method for the copula regression models with/without covariates.
=======
You can see ``rMGLReg`` in action at https://lizhengxiao.github.io/rMGLReg/: 
this is the output of Rdocumentation applied to the latest version of ``rMGLReg``.

The goal of R package: ``rMGLReg`` is to 
=======
# rMGLReg
>>>>>>> parent of 0dd254f (v2)

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/lizhengxiao/rMGLReg/branch/main/graph/badge.svg)](https://app.codecov.io/gh/lizhengxiao/rMGLReg?branch=main)
[![R-CMD-check](https://github.com/lizhengxiao/rMGLReg/workflows/R-CMD-check/badge.svg)](https://github.com/lizhengxiao/rMGLReg/actions)
<!-- badges: end -->

The goal of rMGLReg is to 

- provide a nice visualization tool for interpreting the MGL copula and MGL-EV copula, along with its survival copulas.

<<<<<<< HEAD
>>>>>>> parent of 49cec11 (Merge pull request #20 from lizhengxiao/main)
=======
- show the maximum likelihood (ME) estimation method for the copula regression models with/without covariates.
>>>>>>> parent of 0dd254f (v2)


## Installation

<<<<<<< HEAD
<<<<<<< HEAD
You can install the released version of rMGLReg by running the following lines in R software: 

``` {r, eval = FALSE}
install.packages("devtools")
library(devtools)
devtools::install_github("lizhengxiao/rMGLReg")
=======
- You can install the released version of ``rMGLReg`` by running the following lines in R software: 
=======
You can install the released version of rMGLReg by running the following lines in R software: 
>>>>>>> parent of 0dd254f (v2)

``` {r, eval = FALSE}
install.packages("devtools")
library(devtools)
<<<<<<< HEAD
# devtools::install_github("lizhengxiao/rMGLReg")
devtools::install_github("lizhengxiao/rMGLReg", build_vignettes = TRUE, force = TRUE)
```

 
- To access documentation for all the functions present in the package; for example, enter the command:

``` r
library(rMGLReg)
help(package = rMGLReg)
```




- You can see all the installed vignettes in ``rMGLReg`` package with

``` r
browseVignettes(package  = "rMGLReg")
>>>>>>> parent of 49cec11 (Merge pull request #20 from lizhengxiao/main)
=======
devtools::install_github("lizhengxiao/rMGLReg")
>>>>>>> parent of 0dd254f (v2)
```

## Example

### Simuation from the proposed copulas

This is a basic example which shows 
the	normalized scatter plots for ($\delta=1.2$)
			with simulated samples of the 3-dimensional
         MGL copula  and survival MGL copula.

```{r example}
library(rMGLReg)
## basic example code
set.seed(271)
n <- 1000
delta <- 1.2
d <- 3
U <- rcMGL.multi(n = 1000, d = d, pars = delta)
cor(U, method = "kendall")
par(pty = "s")
pairs(U, gap = 0, cex = 0.5)
```

```{r}
set.seed(271)
n <- 1000
delta <- 1.2
d <- 3
U <- rcMGL180.multi(n = 1000, d = d, pars = delta)
cor(U, method = "kendall")
par(pty = "s")
pairs(U, gap = 0, cex = 0.5)
```

### Plots of survival MGL-EV copula

```{r}
library(data.table)
library(ggplot2)
library(latex2exp)
library(metR)
# joint distribution function of survival MGL-EV copula
n.grid <- 200
par.copula <- 1
xgrid <- ygrid <- seq(0.01, 0.99, length.out = n.grid)
grid <- expand.grid("u1" = xgrid, "u2" = ygrid)
mtrx3d <- matrix(0, nrow = nrow(grid), ncol = 3)
mtrx3d <- cbind(grid, 
                "pcu1u2" = pcMGLEV.bivar(u1 = grid[,1], 
                                   u2 = grid[,2], 
                                   param = par.copula)) # evaluate W on 'grid'
mtrx3d <- data.table(u1 = mtrx3d[,1], 
                     u2 = mtrx3d[,2], 
                     pcu1u2 = mtrx3d[,3])
p1 <- ggplot(mtrx3d, aes(u1, u2, z = pcu1u2)) + 
  scale_x_continuous(expand = c(0, 0), limits = c(0, 1)) + 
  scale_y_continuous(expand = c(0, 0), limits = c(0, 1)) + 
  theme_bw() + 
  ggtitle(TeX('Contour plot for cdf of $\\bar{C}^{MGL-EV}$')) + 
  theme(axis.line = element_line(colour = "black"),
        axis.text.x = element_text(margin = margin(t = 0.25, unit = "cm")),
        axis.text.y = element_text(margin = margin(r = 0.25, unit = "cm"),
                                   size = 10, 
                                   vjust = 0.5, 
                                   hjust = 0.5),
        plot.title = element_text(hjust = 0.5)) + 
  labs(x = TeX("$u_1$"), y = TeX("$u_2$"))  + 
  geom_contour(colour = 'black', 
               show.legend = TRUE,
               bins = 10,
               size = 0.8
  ) + 
  geom_text_contour(aes(z = round(pcu1u2, 4)), stroke = 0.2)
# joint density function of survival MGL-EV copula
n.grid <- 200
par.copula <- 1
xgrid <- ygrid <- seq(0.05, 0.95, length.out = n.grid)
grid <- expand.grid("u1" = xgrid, "u2" = ygrid)
mtrx3d <- matrix(0, nrow = nrow(grid), ncol = 3)
mtrx3d <- cbind(grid, 
                "dcu1u2" = dcMGLEV.bivar(u1 = grid[,1], 
                                   u2 = grid[,2], 
                                   param = par.copula)) # evaluate W on 'grid'
head(mtrx3d)
mtrx3d <- data.table(u1 = mtrx3d[,1], 
                     u2 = mtrx3d[,2], 
                     dcu1u2 = mtrx3d[,3])
library(ggplot2)
library(reshape2)
library(metR)
p2 <- ggplot(mtrx3d, aes(u1, u2, z = dcu1u2)) + 
  scale_x_continuous(expand = c(0, 0), limits = c(0, 1)) + 
  scale_y_continuous(expand = c(0, 0), limits = c(0, 1)) + 
  theme_bw() + 
  ggtitle(TeX('Contour plot for pdf of $\\bar{C}^{MGL-EV}$')) + 
  theme(axis.line = element_line(colour = "black"),
        axis.text.x = element_text(margin = margin(t = 0.25, unit = "cm")),
        axis.text.y = element_text(margin = margin(r = 0.25, unit = "cm"),
                                   size = 10, 
                                   vjust = 0.5, 
                                   hjust = 0.5),
        plot.title = element_text(hjust = 0.5)) + 
  labs(x = TeX("$u_1$"), y = TeX("$u_2$"))  + 
  geom_contour(colour = 'black', 
               show.legend = TRUE,
               bins = 15, 
               size = 0.8, 
               linetype = 1
               ) + 
  geom_text_contour(aes(z = round(dcu1u2, 4)), stroke = 0.2)
# the Pickands dependence function of survival MGL-EV copula
delta.vector <- c(0.01, 0.6, 1.5, 2.0, 20)
k.mat <- matrix(0, nrow = 100, ncol = length(delta.vector))
for(i in 1:length(delta.vector)){
  w.vector <- seq(0.0001, 0.9999, length.out = 100)
  k.mat[,i] <- Afunction(w = w.vector, param = delta.vector[i])
}
dtplot <- data.table(w = rep(w.vector, times = length(delta.vector)),
                     delta = factor(rep(delta.vector, each = 100)),
                     k = as.vector(k.mat))
p3 <- ggplot(data = dtplot, 
       mapping = aes(x = w, y = k)) + 
  theme_bw() + xlab(TeX('$w$')) + ylab(TeX('$A(w)$')) + 
  geom_line(aes(linetype = delta), size = 0.8) +
  scale_x_continuous(limits = c(0, 1),
                     breaks = seq(0, 1, by = 0.2)) +
  scale_y_continuous(limits = c(0.5, 1),
                     breaks = seq(0.5, 1, by = 0.1)) +
  ggtitle(TeX('Pickands functions of $\\bar{C}^{MGL-EV}$')) + 
  theme(axis.line = element_line(colour = "black"),
        axis.text.x = element_text(margin = margin(t = 0.25, unit = "cm")),
        axis.text.y = element_text(margin = margin(r = 0.25, unit = "cm"),
                                   size = 10,
                                   vjust = 0.5,
                                   hjust = 0.5),
        axis.ticks.length = unit(-0.1, "cm"),
        plot.title = element_text(hjust = 0.5),
        legend.direction = 'vertical',
        legend.box.just = "right",
        legend.text = element_text(size = 10)
  ) + labs(linetype = TeX('$\\delta$'))
```


```{r, fig.align="center", fig.width=8, fig.height=2.5}
library(patchwork)
p0 <- p1 + p2 + p3 + plot_layout(ncol = 3)
p0
```

### $d=10$-dimensional MGL regression model

```{r}
# simulated data
set.seed(111)
Nsim <- 1000
d <- 10
n <- 1000 # sample size
beta.true <- c(-0.6, 0.5, 0.2) # true regression coefficients
x1 <- rnorm(n, 0, 1)
x2 <- rnorm(n, 0, 1)
X <- model.matrix(~ x1 + x2) # design matrix
delta.sim <- as.vector(exp(X%*%beta.true)) # true copula parameters
Usim <- matrix(0, nrow = n, ncol = d)
for (i in 1:n){
  Usim[i, ] <- rcMGL.multi(n = 1, d = d, pars = delta.sim[i])
}
m.MGLMGA <- MGL.reg(U = Usim, copula = "MGL",
                                 X = X, method = "Nelder-Mead",
                                 initpar = c(-0.32, 0.001, 0.001)
  )
m.MGLMGA
```


<<<<<<< HEAD
<<<<<<< HEAD
=======
>>>>>>> parent of 0dd254f (v2)
### Case - Danish fire data set

- As the first example, we fit the bivariate copula and regression models to 
the Danish fire insurance data set which was
collected from the Copenhagen Reinsurance Company and comprises 2167 fire losses over the period 1980-1990.

```{r}
  library(rMGLReg)
  library(fitdistrplus)
  library(splines)
  library(snpar)
  data("danishmulti")
  dt <- data.table::data.table(danishmulti)
  dtnew <- dt[Building>0&Contents>0]
  y1 <- dtnew$Building
  y2 <- dtnew$Contents
  y <- cbind(y1, y2)
  
  # empirical cdf
  u1 <- snpar::kde(y[,1], kernel = "gaus", 
             xgrid = y[,1],
             h = 0.2)$Fhat
  u2 <- snpar::kde(y[,2], kernel = "gaus", 
             xgrid = y[,2],
             h = 0.2)$Fhat
  U <- cbind(u1, u2) # bivariate pseudo copula data.
```


```{r}
library(ggplot2)
library(latex2exp)
Usample <- U
XY <- y
newtheme <-   theme_bw() + theme(axis.line = element_line(colour = "black"),
                                 axis.text.x = element_text(margin = margin(t = 0.25, unit = "cm")),
                                 axis.text.y = element_text(margin = margin(r = 0.25, unit = "cm"),
                                                            size = 10, 
                                                            vjust = 0.5, 
                                                            hjust = 0.5),
                                 axis.ticks.length = unit(-0.1, "cm"),
                                 plot.title = element_text(hjust = 0.5),
                                 legend.direction = 'vertical',
                                 legend.position = c(.95, .99),
                                 legend.justification = c("right", "top"),
                                 legend.box.just = "right",
                                 legend.text = element_text(size = 10)) 

dtplot <- data.frame(U1 = Usample[,1], U2 = Usample[,2],
                     logY1 = log(XY[,1]), logY2 = log(XY[,2]))

p1 <- ggplot(data = dtplot, mapping = aes(y = logY1, 
                                          x = logY2)) + 
  newtheme +
  geom_point() + 
  labs(title = "", 
       x = TeX("$log Y_1$"), 
       y = TeX("$log Y_2$")) +  
  scale_x_continuous(limits = c(-7.5, 5),
                     breaks = seq(-7.5, 5, by = 2.5)) +
  scale_y_continuous(limits = c(-5, 5),
                     breaks = seq(-5, 5, by = 2.5))



p2 <- ggplot(data = dtplot, mapping = aes(y = U2, 
                                           x = U1)) + 
  newtheme +
  geom_point() + 
  labs(title = "", 
     x = TeX("$u_1$"), 
     y = TeX("$u_2$")) +  
  scale_x_continuous(limits = c(0, 1),
                     breaks = seq(0, 1, by = 0.2)) +
  scale_y_continuous(limits = c(0, 1),
                     breaks = seq(0, 1, by = 0.2))


library(patchwork)
p0 <- p1 + p2 + plot_layout(ncol = 2)
p0

```


- This table reports the estimation results, AIC and BIC values of the survival MGL and the survival MGL-EV copula, along with four other families of copulas with
positive upper tail indices,  the MGB2 copula,
the Gumbel copula,  the Student $t$ copula, and the Gaussian copula.

```{r, eval = TRUE}
m.norm <- MGL.mle(U = U,
                        copula  = "Normal",
                        initpar = 0.5)

m.t <- MGL.mle(U = U,
                     copula  = "t",
                     initpar = c(0.5, 4))
m.gumbel <- MGL.mle(U = U,
                     copula  = "Gumbel",
                          initpar = c(2))
m.MGLMGA180 <- MGL.mle(U,
                    copula  = "MGL180",
                             initpar = c(1))
m.MGB2 <- MGL.mle(U,
                      copula  = "MGB2",
                        initpar = c(0.1, 2, 0.4))

m.MGLEV180 <- MGL.mle(U,
                         copula  = "MGL-EV180",
                         initpar = c(2))

recap <- function(x){
  res <- c(alpha = x$estimates,
           se = x$se,
           loglike = x$loglike,
           AIC = x$AIC, BIC = x$BIC)
  if(length(res) < 6)
    res <- c(res[1], NA, NA,res[2], NA, NA, res[3:5])
  if (length(res) > 6 & length(res) < 9)
    res <- c(res[1:2], NA, res[3:4], NA, res[5:7])
  res <- as.matrix(res)
  colnames(res) <- x$copula$name
  res}
res.all <- round(cbind(recap(m.norm),
                       recap(m.t),
                       recap(m.gumbel),
                       recap(m.MGLMGA180),
                       recap(m.MGB2),
                       recap(m.MGLEV180)
), 4)
out.com <- t(res.all)
out.com <- out.com[order(out.com[,9], decreasing = T),]
knitr::kable(out.com, digits = 3)


```


- We further investigate the dynamic dependence introducing the covariate \textit{{Year}} into the dependence parameter in the survival MGL and survival MGL-EV regression model respectively.


```{r}

  dtnew[, year := as.numeric(substr(Date, start = 1, stop = 4))]
  dtnew[, x1 := (year - mean(year))/(sd(year))]
  dtnew[, day := difftime(as.Date(Date), as.Date("1980-01-03"), units="days")]

  X <- splines::ns(dtnew$year, knots = quantile(dtnew$year, c(0.5)), intercept = T)

  
  m.MGL180 <- MGL.reg(U = U, copula = "MGL180",
                                 X = X, method = "Nelder-Mead",
                                 initpar = c(-0.32, 0.001, 0.001)
  )
  # survival MGL-EV copual regression
  m.MGLEV180 <- MGL.reg(U = U, copula = "MGL-EV180",
                         method = "Nelder-Mead",
                         X = X,
                         initpar = c(-0.32, 0.001, 0.001)
  )
  
  
  

```


- The predicted value of copula parameter with different value of the covariate \textit{Year} for the Danish fire insurance data set.

```{r}

# Survival MGL regression model
par.est <- m.MGL180$estimates
agepred <- seq(from = 1980, to = 1990)
Xcopula <-  splines::ns(agepred, knots = quantile(dtnew$year, c(0.5)), intercept = T)
delta.est <- exp(Xcopula%*%par.est)
cov.est <- -solve(m.MGL180$hessian)
beta.sim <- matrix(0, nrow = 100, ncol = 4)
delta.mat <- matrix(0, nrow = length(agepred), ncol = 100)
beta.sim <- mvrnorm(100, mu = par.est, Sigma = cov.est)
for(i in 1:100){
  delta.mat[,i] <- exp(Xcopula%*%beta.sim[i,])
}
matplot(delta.mat, col = 'gray', type = 'l', ylim = c(0, 2), main = 'Survival MGL')
lines(delta.est, col = 'red', lwd = 2)



# Surivial MGL-EV regression
par.est <- m.MGLEV180$estimates
agepred <- seq(from = 1980, to = 1990)
Xcopula <-  ns(agepred, knots = quantile(dtnew$year, c(0.5)), intercept = T)
delta.est <- exp(Xcopula%*%par.est)
cov.est <- -solve(m.MGLEV180$hessian)
beta.sim <- matrix(0, nrow = 100, ncol = 4)
delta.mat <- matrix(0, nrow = length(agepred), ncol = 100)
beta.sim <- mvrnorm(100, mu = par.est, Sigma = cov.est)
for(i in 1:100){
  delta.mat[,i] <- exp(Xcopula%*%beta.sim[i,])
}
matplot(delta.mat, col = 'gray', type = 'l', ylim = c(0, 2), main = 'Survival MGL-EV')
lines(delta.est, col = 'red', lwd = 2)

```
<<<<<<< HEAD
=======
<!-- ### Case - Danish fire data set -->

<!-- - As the first example, we fit the bivariate copula and regression models to  -->
<!-- the Danish fire insurance data set which was -->
<!-- collected from the Copenhagen Reinsurance Company and comprises 2167 fire losses over the period 1980-1990. -->

<!-- ```{r} -->
<!--   library(rMGLReg) -->
<!--   library(fitdistrplus) -->
<!--   library(splines) -->
<!--   library(snpar) -->
<!--   data("danishmulti") -->
<!--   dt <- data.table::data.table(danishmulti) -->
<!--   dtnew <- dt[Building>0&Contents>0] -->
<!--   y1 <- dtnew$Building -->
<!--   y2 <- dtnew$Contents -->
<!--   y <- cbind(y1, y2) -->

<!--   # empirical cdf -->
<!--   u1 <- snpar::kde(y[,1], kernel = "gaus",  -->
<!--              xgrid = y[,1], -->
<!--              h = 0.2)$Fhat -->
<!--   u2 <- snpar::kde(y[,2], kernel = "gaus",  -->
<!--              xgrid = y[,2], -->
<!--              h = 0.2)$Fhat -->
<!--   U <- cbind(u1, u2) # bivariate pseudo copula data. -->
<!-- ``` -->


<!-- ```{r} -->
<!-- library(ggplot2) -->
<!-- library(latex2exp) -->
<!-- Usample <- U -->
<!-- XY <- y -->
<!-- newtheme <-   theme_bw() + theme(axis.line = element_line(colour = "black"), -->
<!--                                  axis.text.x = element_text(margin = margin(t = 0.25, unit = "cm")), -->
<!--                                  axis.text.y = element_text(margin = margin(r = 0.25, unit = "cm"), -->
<!--                                                             size = 10,  -->
<!--                                                             vjust = 0.5,  -->
<!--                                                             hjust = 0.5), -->
<!--                                  axis.ticks.length = unit(-0.1, "cm"), -->
<!--                                  plot.title = element_text(hjust = 0.5), -->
<!--                                  legend.direction = 'vertical', -->
<!--                                  legend.position = c(.95, .99), -->
<!--                                  legend.justification = c("right", "top"), -->
<!--                                  legend.box.just = "right", -->
<!--                                  legend.text = element_text(size = 10))  -->

<!-- dtplot <- data.frame(U1 = Usample[,1], U2 = Usample[,2], -->
<!--                      logY1 = log(XY[,1]), logY2 = log(XY[,2])) -->

<!-- p1 <- ggplot(data = dtplot, mapping = aes(y = logY1,  -->
<!--                                           x = logY2)) +  -->
<!--   newtheme + -->
<!--   geom_point() +  -->
<!--   labs(title = "",  -->
<!--        x = TeX("$log Y_1$"),  -->
<!--        y = TeX("$log Y_2$")) +   -->
<!--   scale_x_continuous(limits = c(-7.5, 5), -->
<!--                      breaks = seq(-7.5, 5, by = 2.5)) + -->
<!--   scale_y_continuous(limits = c(-5, 5), -->
<!--                      breaks = seq(-5, 5, by = 2.5)) -->



<!-- p2 <- ggplot(data = dtplot, mapping = aes(y = U2,  -->
<!--                                            x = U1)) +  -->
<!--   newtheme + -->
<!--   geom_point() +  -->
<!--   labs(title = "",  -->
<!--      x = TeX("$u_1$"),  -->
<!--      y = TeX("$u_2$")) +   -->
<!--   scale_x_continuous(limits = c(0, 1), -->
<!--                      breaks = seq(0, 1, by = 0.2)) + -->
<!--   scale_y_continuous(limits = c(0, 1), -->
<!--                      breaks = seq(0, 1, by = 0.2)) -->


<!-- library(patchwork) -->
<!-- p0 <- p1 + p2 + plot_layout(ncol = 2) -->
<!-- p0 -->

<!-- ``` -->


<!-- - This table reports the estimation results, AIC and BIC values of the survival MGL and the survival MGL-EV copula, along with four other families of copulas with -->
<!-- positive upper tail indices,  the MGB2 copula, -->
<!-- the Gumbel copula,  the Student $t$ copula, and the Gaussian copula. -->

<!-- ```{r, eval = TRUE} -->
<!-- m.norm <- MGL.mle(U = U, -->
<!--                         copula  = "Normal", -->
<!--                         initpar = 0.5) -->

<!-- m.t <- MGL.mle(U = U, -->
<!--                      copula  = "t", -->
<!--                      initpar = c(0.5, 4)) -->
<!-- m.gumbel <- MGL.mle(U = U, -->
<!--                      copula  = "Gumbel", -->
<!--                           initpar = c(2)) -->
<!-- m.MGLMGA180 <- MGL.mle(U, -->
<!--                     copula  = "MGL180", -->
<!--                              initpar = c(1)) -->
<!-- m.MGB2 <- MGL.mle(U, -->
<!--                       copula  = "MGB2", -->
<!--                         initpar = c(0.1, 2, 0.4)) -->

<!-- m.MGLEV180 <- MGL.mle(U, -->
<!--                          copula  = "MGL-EV180", -->
<!--                          initpar = c(2)) -->

<!-- recap <- function(x){ -->
<!--   res <- c(alpha = x$estimates, -->
<!--            se = x$se, -->
<!--            loglike = x$loglike, -->
<!--            AIC = x$AIC, BIC = x$BIC) -->
<!--   if(length(res) < 6) -->
<!--     res <- c(res[1], NA, NA,res[2], NA, NA, res[3:5]) -->
<!--   if (length(res) > 6 & length(res) < 9) -->
<!--     res <- c(res[1:2], NA, res[3:4], NA, res[5:7]) -->
<!--   res <- as.matrix(res) -->
<!--   colnames(res) <- x$copula$name -->
<!--   res} -->
<!-- res.all <- round(cbind(recap(m.norm), -->
<!--                        recap(m.t), -->
<!--                        recap(m.gumbel), -->
<!--                        recap(m.MGLMGA180), -->
<!--                        recap(m.MGB2), -->
<!--                        recap(m.MGLEV180) -->
<!-- ), 4) -->
<!-- out.com <- t(res.all) -->
<!-- out.com <- out.com[order(out.com[,9], decreasing = T),] -->
<!-- knitr::kable(out.com, digits = 3) -->


<!-- ``` -->


<!-- - We further investigate the dynamic dependence introducing the covariate \textit{{Year}} into the dependence parameter in the survival MGL and survival MGL-EV regression model respectively. -->


<!-- ```{r} -->

<!--   dtnew[, year := as.numeric(substr(Date, start = 1, stop = 4))] -->
<!--   dtnew[, x1 := (year - mean(year))/(sd(year))] -->
<!--   dtnew[, day := difftime(as.Date(Date), as.Date("1980-01-03"), units="days")] -->

<!--   X <- splines::ns(dtnew$year, knots = quantile(dtnew$year, c(0.5)), intercept = T) -->


<!--   m.MGL180 <- MGL.reg(U = U, copula = "MGL180", -->
<!--                                  X = X, method = "Nelder-Mead", -->
<!--                                  initpar = c(-0.32, 0.001, 0.001) -->
<!--   ) -->
<!--   # survival MGL-EV copual regression -->
<!--   m.MGLEV180 <- MGL.reg(U = U, copula = "MGL-EV180", -->
<!--                          method = "Nelder-Mead", -->
<!--                          X = X, -->
<!--                          initpar = c(-0.32, 0.001, 0.001) -->
<!--   ) -->




<!-- ``` -->


<!-- - The predicted value of copula parameter with different value of the covariate \textit{Year} for the Danish fire insurance data set. -->

<!-- ```{r} -->

<!-- # Survival MGL regression model -->
<!-- par.est <- m.MGL180$estimates -->
<!-- agepred <- seq(from = 1980, to = 1990) -->
<!-- Xcopula <-  splines::ns(agepred, knots = quantile(dtnew$year, c(0.5)), intercept = T) -->
<!-- delta.est <- exp(Xcopula%*%par.est) -->
<!-- cov.est <- -solve(m.MGL180$hessian) -->
<!-- beta.sim <- matrix(0, nrow = 100, ncol = 4) -->
<!-- delta.mat <- matrix(0, nrow = length(agepred), ncol = 100) -->
<!-- beta.sim <- mvrnorm(100, mu = par.est, Sigma = cov.est) -->
<!-- for(i in 1:100){ -->
<!--   delta.mat[,i] <- exp(Xcopula%*%beta.sim[i,]) -->
<!-- } -->
<!-- matplot(delta.mat, col = 'gray', type = 'l', ylim = c(0, 2), main = 'Survival MGL') -->
<!-- lines(delta.est, col = 'red', lwd = 2) -->



<!-- # Surivial MGL-EV regression -->
<!-- par.est <- m.MGLEV180$estimates -->
<!-- agepred <- seq(from = 1980, to = 1990) -->
<!-- Xcopula <-  ns(agepred, knots = quantile(dtnew$year, c(0.5)), intercept = T) -->
<!-- delta.est <- exp(Xcopula%*%par.est) -->
<!-- cov.est <- -solve(m.MGLEV180$hessian) -->
<!-- beta.sim <- matrix(0, nrow = 100, ncol = 4) -->
<!-- delta.mat <- matrix(0, nrow = length(agepred), ncol = 100) -->
<!-- beta.sim <- mvrnorm(100, mu = par.est, Sigma = cov.est) -->
<!-- for(i in 1:100){ -->
<!--   delta.mat[,i] <- exp(Xcopula%*%beta.sim[i,]) -->
<!-- } -->
<!-- matplot(delta.mat, col = 'gray', type = 'l', ylim = c(0, 2), main = 'Survival MGL-EV') -->
<!-- lines(delta.est, col = 'red', lwd = 2) -->

<!-- ``` -->
>>>>>>> parent of 49cec11 (Merge pull request #20 from lizhengxiao/main)
=======
>>>>>>> parent of 0dd254f (v2)



