---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rMGLReg

<!-- badges: start -->
<!-- badges: end -->

The goal of rMGLReg is to 

- provide a nice visualization tool for interpreting the MGL copula and MGL-EV copula, along with its survival copulas.

- show the maximum likelihood (ME) estimation method for the copula regression models with/without covariates.


## Installation

You can install the released version of rMGLReg by running the following lines in R software: 

``` {r, eval = FALSE}
install.packages("devtools")
library(devtools)
devtools::install_github("lizhengxiao/rMGLReg")
```

## Example

### Simuation from the proposed copulas

This is a basic example which shows 
the	normalized scatter plots for ($\delta=1.2$)
			with simulated samples of the 3-dimensional
         MGL copula  and survival MGL copula.

```{r example}
library(rMGLReg)
## basic example code
set.seed(271)
n <- 1000
delta <- 1.2
d <- 3
U <- rcMGL.multi(n = 1000, d = d, pars = delta)
cor(U, method = "kendall")
par(pty = "s")
pairs(U, gap = 0, cex = 0.5)
```

```{r}
set.seed(271)
n <- 1000
delta <- 1.2
d <- 3
U <- rcMGL180.multi(n = 1000, d = d, pars = delta)
cor(U, method = "kendall")
par(pty = "s")
pairs(U, gap = 0, cex = 0.5)
```


### Case I - Danish fire data set

As the first example, we fit the bivariate copula and  regression models to 
the Danish fire insurance data set which was
collected from the Copenhagen Reinsurance Company and comprises 2167 fire losses over the period 1980-1990.

```{r}
  library(rMGLReg)
  library(fitdistrplus)
  library(splines)
  library(snpar)
  data("danishmulti")
  dt <- data.table::data.table(danishmulti)
  dtnew <- dt[Building>0&Contents>0]
  y1 <- dtnew$Building
  y2 <- dtnew$Contents
  y <- cbind(y1, y2)
  
  # empirical cdf
  u1 <- snpar::kde(y[,1], kernel = "gaus", 
             xgrid = y[,1],
             h = 0.2)$Fhat
  u2 <- snpar::kde(y[,2], kernel = "gaus", 
             xgrid = y[,2],
             h = 0.2)$Fhat
  U <- cbind(u1, u2) # bivariate pseudo copula data.
```


```{r}
library(ggplot2)
library(latex2exp)
Usample <- U
XY <- y
newtheme <-   theme_bw() + theme(axis.line = element_line(colour = "black"),
                                 axis.text.x = element_text(margin = margin(t = 0.25, unit = "cm")),
                                 axis.text.y = element_text(margin = margin(r = 0.25, unit = "cm"),
                                                            size = 10, 
                                                            vjust = 0.5, 
                                                            hjust = 0.5),
                                 axis.ticks.length = unit(-0.1, "cm"),
                                 plot.title = element_text(hjust = 0.5),
                                 legend.direction = 'vertical',
                                 legend.position = c(.95, .99),
                                 legend.justification = c("right", "top"),
                                 legend.box.just = "right",
                                 legend.text = element_text(size = 10)) 

dtplot <- data.frame(U1 = Usample[,1], U2 = Usample[,2],
                     logY1 = log(XY[,1]), logY2 = log(XY[,2]))

p1 <- ggplot(data = dtplot, mapping = aes(y = logY1, 
                                          x = logY2)) + 
  newtheme +
  geom_point() + 
  labs(title = "", 
       x = TeX("$log Y_1$"), 
       y = TeX("$log Y_2$")) +  
  scale_x_continuous(limits = c(-7.5, 5),
                     breaks = seq(-7.5, 5, by = 2.5)) +
  scale_y_continuous(limits = c(-5, 5),
                     breaks = seq(-5, 5, by = 2.5))



p2 <- ggplot(data = dtplot, mapping = aes(y = U2, 
                                           x = U1)) + 
  newtheme +
  geom_point() + 
  labs(title = "", 
     x = TeX("$u_1$"), 
     y = TeX("$u_2$")) +  
  scale_x_continuous(limits = c(0, 1),
                     breaks = seq(0, 1, by = 0.2)) +
  scale_y_continuous(limits = c(0, 1),
                     breaks = seq(0, 1, by = 0.2))


library(patchwork)
p0 <- p1 + p2 + plot_layout(ncol = 2)
p0

```


This table reports the estimation results, AIC and BIC values of the survival MGL and the survival MGL-EV copula, along with four other families of copulas with
positive upper tail indices,  the MGB2 copula,
the Gumbel copula,  the Student $t$ copula, and the Gaussian copula.

```{r, eval = TRUE}
m.norm <- MGL.mle(U = U,
                        copula  = "Normal",
                        initpar = 0.5)

m.t <- MGL.mle(U = U,
                     copula  = "t",
                     initpar = c(0.5, 4))
m.gumbel <- MGL.mle(U = U,
                     copula  = "Gumbel",
                          initpar = c(2))
m.MGLMGA180 <- MGL.mle(U,
                    copula  = "MGL180",
                             initpar = c(1))
m.MGB2 <- MGL.mle(U,
                      copula  = "MGB2",
                        initpar = c(0.1, 2, 0.4))

m.MGLEV180 <- MGL.mle(U,
                         copula  = "MGL-EV180",
                         initpar = c(2))

recap <- function(x){
  res <- c(alpha = x$estimates,
           se = x$se,
           loglike = x$loglike,
           AIC = x$AIC, BIC = x$BIC)
  if(length(res) < 6)
    res <- c(res[1], NA, NA,res[2], NA, NA, res[3:5])
  if (length(res) > 6 & length(res) < 9)
    res <- c(res[1:2], NA, res[3:4], NA, res[5:7])
  res <- as.matrix(res)
  colnames(res) <- x$copula$name
  res}
res.all <- round(cbind(recap(m.norm),
                       recap(m.t),
                       recap(m.gumbel),
                       recap(m.MGLMGA180),
                       recap(m.MGB2),
                       recap(m.MGLEV180)
), 4)
out.com <- t(res.all)
out.com <- out.com[order(out.com[,9], decreasing = T),]
knitr::kable(out.com, digits = 3)


```

We further investigate the dynamic dependence introducing the covariate \textit{{Year}} into the dependence parameter in the survival MGL and survival MGL-EV regression model respectively.


```{r}

  dtnew[, year := as.numeric(substr(Date, start = 1, stop = 4))]
  dtnew[, x1 := (year - mean(year))/(sd(year))]
  dtnew[, day := difftime(as.Date(Date), as.Date("1980-01-03"), units="days")]

  X <- splines::ns(dtnew$year, knots = quantile(dtnew$year, c(0.5)), intercept = T)

  
  m.MGL180 <- MGL.reg(U = U, copula = "MGL180",
                                 X = X, method = "Nelder-Mead",
                                 initpar = c(-0.32, 0.001, 0.001)
  )
  # survival MGL-EV copual regression
  m.MGLEV180 <- MGL.reg(U = U, copula = "MGL-EV180",
                         method = "Nelder-Mead",
                         X = X,
                         initpar = c(-0.32, 0.001, 0.001)
  )
  
  
  

```


The predicted value of copula parameter with different value of the covariate \textit{Year} for the Danish fire insurance data set.

```{r}

# Survival MGL regression model
par.est <- m.MGL180$estimates
agepred <- seq(from = 1980, to = 1990)
Xcopula <-  splines::ns(agepred, knots = quantile(dtnew$year, c(0.5)), intercept = T)
delta.est <- exp(Xcopula%*%par.est)
cov.est <- -solve(m.MGL180$hessian)
beta.sim <- matrix(0, nrow = 100, ncol = 4)
delta.mat <- matrix(0, nrow = length(agepred), ncol = 100)
beta.sim <- mvrnorm(100, mu = par.est, Sigma = cov.est)
for(i in 1:100){
  delta.mat[,i] <- exp(Xcopula%*%beta.sim[i,])
}
matplot(delta.mat, col = 'gray', type = 'l', ylim = c(0, 2), main = 'Survival MGL')
lines(delta.est, col = 'red', lwd = 2)



# Surivial MGL-EV regression
par.est <- m.MGLEV180$estimates
agepred <- seq(from = 1980, to = 1990)
Xcopula <-  ns(agepred, knots = quantile(dtnew$year, c(0.5)), intercept = T)
delta.est <- exp(Xcopula%*%par.est)
cov.est <- -solve(m.MGLEV180$hessian)
beta.sim <- matrix(0, nrow = 100, ncol = 4)
delta.mat <- matrix(0, nrow = length(agepred), ncol = 100)
beta.sim <- mvrnorm(100, mu = par.est, Sigma = cov.est)
for(i in 1:100){
  delta.mat[,i] <- exp(Xcopula%*%beta.sim[i,])
}
matplot(delta.mat, col = 'gray', type = 'l', ylim = c(0, 2), main = 'Survival MGL-EV')
lines(delta.est, col = 'red', lwd = 2)

```



